### 2018-01-03 icde/revision/sec-alg.tex

\stitle{Block-wise algorithm~\twprscc}.  It takes as input a citation or venue graph $G(V, E)$ and an iteration threshold $\epsilon$, and returns the TWPageRank vector of $PR$ of $G$.
%To process an \scc instead of the entire graph,
To update scores of nodes in an \scc at a time, the edges of $G$ are partitioned into: (a) the set $E_i$ of edges inside \sccs and (b) the set $E_a$ of edges across \sccs  such that $E_i\cap E_a = \emptyset$ and $E = E_i \cup E_a$.  The update rule in Eq.~(\ref{eq-twpr-update})  is revised accordingly to separate $E$ into $E_i$ and $E_a$  as follows.

\vspace{-1ex}
\begin{scriptsize}
\begin{equation}\label{eq-prscc}
%\begin{split}
PR(v) =  d \sum_{(u,v)\in E_i} M_{u,v} PR(u)
   + d \sum_{(u,v)\in E_a} M_{u,v} PR(u) +  \frac{1-d}{n}.
%\end{split}
\end{equation}
\end{scriptsize}
%
\noindent
It first computes the block-wise graph $G'$ by treating \sccs in $G$ as single nodes, and derives a topological order $O$ of nodes in $G'$. It then processes each \scc in the topological order  $O$ with Eq.~(\ref{eq-prscc}). Finally, it returns the TWPageRank vector. When processing an \scc, it iteratively updates the TWPageRank scores of the nodes in the \scc, and the iteration continues until the sum changes of of TWPageRank scores is less than $\epsilon |scc|/|V|$, where $|scc|$ is the number of nodes in the \scc. Note that there must exist a topological order $O$, as the block-wise graph is a directed acyclic graph~\cite{CormenLRS01}.

@@

\vspace{-1ex}
\stitle{Analysis of algorithm \twprscc}. While similar block-wise algorithms were originally proposed for Web graphs~\cite{Berkhin05}, we next show that they are even better for the TWPageRank computation associated with scholarly data.
%
Given inpute graph $G(V, E)$, the block-wise graph and its topological order can be computed in $O(|V|+|E|)$ time~\cite{CormenLRS01}, and the edges in $E_a$ are only scanned once when updating TWPageRank scores.
From these, we have the following.

>>>>

\stitle{Block-wise algorithm~\twprscc}.  It takes as input a citation or venue graph $G(V, E)$ and an iteration threshold $\epsilon$, and returns the TWPageRank vector $PR$ of $G$.
%To process an \scc instead of the entire graph,
To update scores of nodes in an \scc at a time, the edges of $G$ are partitioned into: (a) the set $E_i$ of edges inside \sccs and (b) the set $E_a$ of edges across \sccs  such that $E_i\cap E_a = \emptyset$ and $E = E_i \cup E_a$.  The update rule in Eq.~(\ref{eq-twpr-update})  is revised accordingly to separate $E$ into $E_i$ and $E_a$  as follows.

\vspace{-1ex}
\begin{scriptsize}
\begin{equation}\label{eq-prscc}
%\begin{split}
PR(v) =  d \sum_{(u,v)\in E_i} M_{u,v} PR(u)
   + d \sum_{(u,v)\in E_a} M_{u,v} PR(u) +  \frac{1-d}{n}.
%\end{split}
\end{equation}
\end{scriptsize}
%
\noindent
It first computes the block-wise graph $G'$ by treating \sccs in $G$ as single nodes, and derives a topological order $O$ of nodes in $G'$. It then processes each \scc in the topological order  $O$ with Eq.~(\ref{eq-prscc}). Finally, it returns the TWPageRank vector. When processing an \scc, it iteratively updates the TWPageRank scores of the nodes in the \scc, and the iteration continues until the sum changes of TWPageRank scores is less than $\epsilon |scc|/|V|$, where $|scc|$ is the number of nodes in the \scc. Note that there must exist a topological order $O$, as the block-wise graph is a directed acyclic graph~\cite{CormenLRS01}.

@@

\vspace{-0.5ex}
\stitle{Analysis of algorithm \twprscc}. While similar block-wise algorithms were originally proposed for Web graphs~\cite{Berkhin05}, we next show that they are even better for the TWPageRank computation associated with scholarly data.
%
Given inpute graph $G(V, E)$, the block-wise graph and its topological order can be computed in $O(|V|+|E|)$ time~\cite{CormenLRS01}, and the edges in $E_a$ are only scanned once when updating TWPageRank scores.
From these, we have the following.
